Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
pf <-read.delim('pseudo_facebook.tsv')
qplot(x=age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point()+
  xlim(13,90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha=1/20 )+
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha=1/20,position = position_jitter(h = 0)  )+
  xlim(13,90)+
  coord_trans(y="sqrt")
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf)+
  geom_point(alpha=1/20,position = position_jitter(h = 0)  )+
  xlim(13,90)
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r}
install.packages('dplyr')
library('dplyr')
```

```{r Conditional Means}

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n=n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)

head(pf.fc_by_age)
#filter()
#group_by()
#mutate()
#arrange()
```
```{r}
pf.fc_by_age2<- pf%>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n=n()) %>%
  arrange(age)

head(pf.fc_by_age2)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(data = pf.fc_by_age,aes(x=age, y = friend_count_mean))+
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf)+
  geom_point(alpha=1/20,
             position = position_jitter(h = 0),
             color = "orange")+
  coord_cartesian(xlim = c(13,90))+
  coord_trans(y = "sqrt")+
  geom_line(stat = "summary", fun.y = mean)+
  geom_line(stat = 'summary', fun.y = quantile, fun.args= list(probs = .1), linetype = 2, color = 'blue')+
  geom_line(stat = 'summary', fun.y = quantile, fun.args= list(probs = .5), linetype = 3, color = 'blue')+
  geom_line(stat = 'summary', fun.y = quantile, fun.args= list(probs = .9), linetype = 2, color = 'blue')



```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor(pf$age,pf$friend_count)

with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(  subset(pf,pf$age<=70) , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf )+
  geom_point()+
  xlim(0,quantile(pf$www_likes_received, 0.95))+
  ylim(0,quantile(pf$likes_received, 0.95))+
  geom_smooth(method = 'lim', color = 'red')


```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(data = pf, cor.test(www_likes_received, likes_received))
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}
data("Mitchell")
mi <- Mitchell
ggplot(aes(x=Temp,y=Month), data = mi)+
  geom_point()
  
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(data =Mitchell, cor.test(Temp,Month))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp))+
  geom_point()+
  scale_x_continuous(breaks = seq(0,203,12))
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age)+
  geom_line()

head(pf.fc_by_age, 10)
pf.fc_by_age[17:19,]
```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_months <- pf$age+(1-pf$dob_month/12)
```

Programming Assignment
```{r Programming Assignment}
PF.FC <- pf%>%
  group_by(age_with_months)%>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n())%>%
  arrange(age_with_months)

head(PF.FC, 10)
options("digits"=5)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
g1 <- ggplot( data = subset(PF.FC, PF.FC$age_with_months<71), aes(x= age_with_months, y = friend_count_mean))+
  geom_line(na.rm = TRUE)

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
g2<- ggplot( data = subset(PF.FC, PF.FC$age_with_months<71), aes(x= age_with_months, y = friend_count_mean))+
  geom_line(na.rm = TRUE)+
  geom_smooth()

g3<- ggplot( data = subset(pf, age<71) , aes(x= round(age/5)*5, y = friend_count))+
  geom_line(stat = 'summary', fun.y = mean,na.rm = TRUE)+
  geom_smooth()


  grid.arrange(g2,g3, ncol = 1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

