# lesson 3 

## Histogram of User's Birthdays

```{r echo = FALSE}

library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
```
## first way
```{r}

names(pf)





```

## second way
```{r}

ggplot(aes(x = dob_day), data = pf)+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks = 1:31)+
  theme_set(theme_minimal(24))+
  facet_wrap(~dob_month, ncol = 3)
  

```

facet_wrap(~dob_month, ncol = 3)
or using facet_grid(~dob_month)

```{r}
ggplot(data = subset(pf, !is.na(gender)), aes(x = friend_count))+
  geom_histogram()+
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0,1000,50))+
  facet_wrap(~gender)
  
qplot( x=friend_count, data = subset(pf, !is.na(gender)), xlim = c(0,1000))+
  facet_grid(.~gender )

qplot(x=friend_count, data = na.omit(pf), binwidth = 25)+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))
```
```{r}
table(pf$gender)
by(pf$friend_count,pf$gender, summary)


```

```{r}
qplot(x=tenure/365, data = pf, 
      xlab = "Number of years using Facebook",
      ylab = "Number of users in sample",
      binwidth =0.25,
      color = I('black'), fill = I('#099dd9'))+
  scale_x_continuous(breaks=seq(1,7,1), limits = c(0,7))
```

```{r}
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```
```{r}
ggplot(aes(x = tenure/365), data = pf) + 
   geom_histogram(binwidth = .25, color = 'black', fill = '#F79420')
```
```{r}
ggplot(aes(x = tenure / 365), data = pf) + 
  geom_histogram(color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) + 
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```
```{r}
ggplot(aes(x=age),data = pf)+
  geom_histogram(binwidth = 1, color = "black", fill = "blue" )+
  scale_x_continuous(breaks = seq(0,120,10), limits = c(10,120))
```

par(mfrow=c(2,2))
plot(wt,mpg, main="Scatterplot of wt vs. mpg")
plot(wt,disp, main="Scatterplot of wt vs disp")
hist(wt, main="Histogram of wt")
boxplot(wt, main="Boxplot of wt")

```{r}
p1 <- ggplot(aes(x=friend_count), data = pf)+
  geom_histogram()

  
p2 <- p1+scale_x_log10()

p3 <- p1+scale_x_sqrt()

# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=1)
```

```{r}
p4 <- qplot(x=friend_count, data = pf)
p5 <- qplot(x=log10(friend_count), data = pf)
p6 <- qplot(x=sqrt(friend_count), data = pf)

p7 <- qplot(x=friend_count, data = pf)+
  scale_x_log10()


grid.arrange(p4, p5, p6, ncol=1)
```
```{r}
grid.arrange(p2, p5, ncol=2)
```

## Frequency Polygons
```{r}
FreqPoly0 <- qplot(x=friend_count, 
      data = subset(pf, !is.na(gender)),
      xlab = 'Friend Count',
      ylab = 'Percentage of users with that friend count',
      binwidth=10, geom = 'freqpoly', color = gender)+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))

FreqPoly1 <- qplot(x=friend_count, y = ..count../sum(..count..), 
      data = subset(pf, !is.na(gender)),
      xlab = 'Friend Count',
      ylab = 'Percentage of users with that friend count',
      binwidth=10, geom = 'freqpoly', color = gender)+
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000,50))

FreqPoly2 <- ggplot(aes(x = friend_count, y = ..count../sum(..count..)),
                    data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')

grid.arrange(FreqPoly0,FreqPoly1, FreqPoly2, ncol=3)
```

```{r}
 ggplot(aes(x = likes, y = ..count../sum(..count..)),
                    data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('likes Count') + 
  ylab('Percentage of users with that likes')


```
```{r}
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()
```
```{r}
by(pf$www_likes,pf$gender,sum)
```

## boxplot
```{r}
box1 <- qplot(x=gender,
      y=friend_count,
      data = subset(pf, !is.na(gender)),
      xlab = 'Friend Count',
      ylab = 'Percentage of users with that friend count',
      geom = 'boxplot')+
  scale_y_continuous(limits = c(0,1000))

box2 <- qplot(x=gender,
      y=friend_count,
      data = subset(pf, !is.na(gender)),
      xlab = 'Friend Count',
      ylab = 'Percentage of users with that friend count',
      geom = 'boxplot')+
  coord_cartesian(ylim=c(0,1000))

grid.arrange(box1,box2,ncol=2)

```
box 2 is better , box1 may dis count some data that out of lim

```{r}
box2 <- qplot(x=gender,
      y=friend_count,
      data = subset(pf, !is.na(gender)),
      xlab = 'Friend Count',
      ylab = 'Percentage of users with that friend count',
      geom = 'boxplot')+
  coord_cartesian(ylim=c(0,250))

by(pf$friend_count,pf$gender,summary)
```

## friendships_initiated
```{r}
fi <- ggplot(data=subset(pf, !is.na(gender)), aes(x=gender,y=friendships_initiated))+
  geom_boxplot(outlier.colour="red", outlier.shape=8, outlier.size=4)+
  coord_flip()+
  coord_cartesian(ylim=c(0,300))
fi
by(pf$friendships_initiated,pf$gender,summary)
```
## Getting Logical
```{r}
summary(pf$mobile_likes)
summary(pf$mobile_likes>0)
pf$moblie_check_in <- NA 
pf$moblie_check_in <- ifelse(pf$mobile_likes>0,1,0)
pf$moblie_check_in <- factor(pf$moblie_check_in)

sum(pf$moblie_check_in==1)/length(pf$moblie_check_in)*100
```


